Contextual Combinatorial Cascading Bandits

### 2016-01-16 contextual combinatorial cascading bandits.tex
update two requirements for general reward

We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}. Let $\cS$ be the set of \textit{feasible actions}. For any feasible action $A \in \cS$, $A$ has an underlying set, which is a subset of $E$, together with a structure $s_A$. In website recommender systems, a feasible action $A$ is a set of $K$ websites listed in linear order and the user, faced with such a website list, will check the website one by one from the beginning. In social influence problem, a feasible action is a subset of people in graph structure. In the rest of the paper, we abuse the notation of $A$ to denote the feasible action and also the corresponding underlying set. We define the {\it size} of feasible action $A$ to be the number of base arms in the underlying set of $A$, denoted by $|A|$. We assume all feasible actions considered in this paper have size at most $K$.

@@

We use random variable $\bw_{t}(a) \in \{0,1\}$ as the {\em weight} of base arm $a$ at time $t$. Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
	\label{eq:expectation}
	\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.

We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$
At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.

>>>>

We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}. Let $\cS$ be the set of \textit{feasible actions}. For any feasible action $A \in \cS$, $A$ has an underlying set, which is a subset of $E$, together with a structure $s_A$. In website recommender systems, a feasible action $A$ is a set of $K$ websites listed in linear order and the user, faced with such a website list, will check the website one by one from the beginning. In social influence problem, a feasible action is a subset of people in graph structure. In the rest of the paper, we abuse the notation of $A$ to denote the feasible action and also the corresponding underlying set. We define the {\it size} of feasible action $A$ to be the number of base arms in the underlying set of $A$, denoted by $|A|$. We assume all feasible actions considered in this paper have size at most $K$. In many of applications, the expected reward of an action relates not only the underlying set but also the structure, or the order of the base arms. For example in recommender systems, to improve user experience, the items with higher preference will be listed higher.

@@

We use random variable $\bw_{t}(a) \in [0,1]$ as the {\em weight} of base arm $a$ at time $t$. Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
	% \label{eq:expectation}
	\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.

The reward function on round $t$ is an application dependent function. We assume the expected reward function $f(A, w)$ of an action $A$ with expected weights $w$ satisfy the following assumptions.

Monotonicity The expected reward $f(A, w)$ is a non-decreasing with respect to $w$. For any $d$ dimension vectors $w$ and $w'$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.

Lipschitz continuity The expected reward function f(A, w) is a Lipschitz continuous with respect to $w$ together with position discount $\gamma$. In particular, there is a constant $B>0$ such that, for any $w$ and $w'$, we have
$$
	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{i \in Ind(A)} \gamma_i^2(w(i) - w'(i))^2}
$$

We don't require the agent knows how the function $f(A, w)$ is defined. We only assume the agent has access to an oracle $O(A, w)$.

% We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
% $$
% \bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
% $$
% or 
% $$
% \bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
% $$
% At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
% Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.

% The agent receives some reward if the user clicks on some item. Suppose we consider the position discount: if the user clicks on the $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$. Usually the importance of the positions is decreasing: the first position is most important. So it is a reasonable assumption that
% $$
% 1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
% $$
% At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
% $$
% \br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
% $$
% where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.

% Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
% \begin{align}
% &f : \cS \times [0,1]^E \to [0,1] \nonumber \\
% &f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
% \label{eq:functionf}
% \end{align}
% Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
% \begin{align*}
% A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
% f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
% \end{align*}
% The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
% $$
% R(T) = \EE\left[\sum_{t=1}^T R(t, \bA_t)\right].
% $$
% where $R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t)$.

% The above formulation is on the disjunctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result. 
% Similarly, we could also consider the case of conjunctive objective. 
% We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}). 
% The learning agent observes all items until the first one with weight $0$. 
% Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$. 
% The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
% $$
% 0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
% $$
% At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward $\br_{\wedge, t}$:
% \begin{align*}
% \br_{\wedge, t} &= \begin{cases}
% \gamma_{\bO_{\wedge, t}}'  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
% 1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
% \end{cases}\\
% &=\begin{cases}
% \gamma_{k}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
% 1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
% \end{cases}
% \end{align*}

% If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
% \begin{align}
% &f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
% &f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
% \label{eq:functionfstar}
% \end{align}
% then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. To simplify notations, we assume 
% $$
% \gamma_k' = 1 - \gamma_k.
% $$
% Then it holds that
% \begin{equation} %eq:ConDisRelation
% \label{eq:ConDisRelation}
% f_{\wedge}(A, w) = 1 - f(A, 1 - w).
% \end{equation}
% Let 
% \begin{align*}
% A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
% f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
% \end{align*}
% For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
% $$
% R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
% $$
% where $R_{\wedge}(t, A) = f_{\wedge, t}^{\ast} - f_{\wedge}(A, \theta_{\ast}^{\top}x_t)$.
